\documentclass{article}

\input{preamble.tex}

\usepackage{parskip}
\usepackage{footmisc}

\begin{document}

\huge Jacob Lawrence

\large Transcript of Mathematics Coursework\hfill \normalsize \textit{Last Updated: \today}

\begin{enumerate}[leftmargin=0in]
    \item[] \textbf{MATH 7720}, \textit{Abstract Algebra}, Fall 2023, Dale Cutkosky \\ 
    Basis properties of integers, fundamental theorem of arithmetic, introduction to groups, rings, and fields.\\
    \textit{Textbook}: \textit{A First Course in Abstract Algebra}, 3rd edition, by Joesph Rotman.  

    \item[] \textbf{MATH 8420}, \textit{Theory of Functions of Real Variables I}\footnote{Part of the Analysis Qualyifing exam sequence\label{Analysis Qual}}, Fall 2023, Carlo Morpurgo\\
    An introduction to the theory of measure and integration, and differentiation.  \\
    \textit{Textbook}: \textit{Real Analysis: Modern Techniques and Their Applications}, 2nd edition, by Gerald B. Folland. 

    \item[] \textbf{MATH 8425}, \textit{Complex Analysis I}, Fall 2023, Tanya Christiansen\\
    Rigorous introduction to the theory of functions of complex variable. Topics include results about complex integration, the maximum modulus theorem (and related results), conformal mappings, infinite products and special functions, analytic continuation, harmonic functions, and further results for zeros of analytic functions. \\
    \textit{Textbook}: \textit{Functions of One Complex Variable I}, 2nd edition, by John B. Conway. 
    
    \item[] \textbf{MATH 7920}, \textit{Advanced Linear Algebra}, Spring 2024, Ian Aberbach\\
    Study of vector spaces over arbitrary fields: topics include maps on finite dimensional vector spaces, bilinear and multilinear forms, invariant subspaces, and canonical forms. \\
    \textit{Textbook}: None.  

    \item[] \textbf{MATH 8421}, \textit{Theory of Functions of Real Variables II}\footref{Analysis Qual}, Spring 2024, Carlo Morpurgo \\
    General measure and integration theory. Elements of the theory of Hilbert and Banach spaces, linear functions, and linear operators. \\
    \textit{Textbook}: \textit{Real Analysis: Modern Techniques and Their Applications}, 2nd edition, by Gerald B. Folland. 

    \item[] \textbf{MATH 8430}, \textit{Differentiable Manifolds}, Spring 2024, Adam Helfer\\
    This course is about calculus in very general settings, which may include curved spaces and abstractly defined spaces. Its origins go back to attempts to make maps of the Earth taking into account its curvature; its modern applications include mechanics, dynamical systems, partial differential equations, and most famously Einstein's theory of gravity. \\
    \textit{Textbook}: None. 

    \item[] \textbf{MATH 8410}, \textit{Algebra I}\footnote{Part of the Algebra Qualifying exam sequence. \label{Algebra Qual}}, Fall 2024, Calin Chindris\\
    Theory of algebraic structures--groups, rings, fields, algebraic and transcendental extensions of fields. \\
    \textit{Textbook}: \textit{Abstract Algebra}, 3rd edition, by David S. Dummit and Richard M. Foote. 
    
    \item[] \textbf{MATH 8630}, \textit{Harmonic Analysis I}, Fall 2024, Steven Hoffman \\
    An introduction to the basic ideas of harmonic analysis in $\R^n$: Hardy-Littlewood Maximal Function, Lebesgue Differentiation, Convolutions and Approximate identities, Fourier transforms, inversions and Plancherel's theorem, Fractional Integration and Soblev spaces, Singular integral Theory and Fourier multipliers, Littlewood-Paley Theory, Fourier restriction and Strichartz estimates, and $BMO$ and $H^1$.\\
    \textit{Textbook}: None.  

    \item[] \textbf{MATH 8445}, \textit{Partial Differential Equations I}, Fall 2024, Samuel Walsh\\
    Fourier and integral transforms, first and second order partial differential equations, methods of characteristics, Laplace's equation, Direchlet and Neumann problems, Green's functions and maximum principles. \\
    \textit{Textbook}: \textit{Partial Differential Equations}, 2nd edition, by Lawrence C. Evans. 

    \item[] \textbf{MATH 8302}, \textit{Topics in Harmonic Analysis (Theory of Distributions)}, Spring 2025, Tanya Christiansen\\
    An introduction to the theory of distributions: Different classes of distributions, operations with distributions, Fourier transform, Schwartz functions and tempered distributions, wavefront sets, and applications. \\
    \textit{Textbook}: \textit{Introduction to the Theory of Distributions}, 2nd edition, by F.G. Friedlander and M. Joshi.
    
    \item[] \textbf{MATH 8411}, \textit{Algebra II} \footref{Algebra Qual}, Spring 2025, Calin Chindris\\
    Cover topics from Fields and Modules and Vector Spaces. \\
    \textit{Textbook}: \textit{Abstract Algebra}, 3rd edition, by David S. Dummit and Richard M. Foote.

    \item[] \textbf{MATH 8631}, \textit{Harmonic Analysis II}, Spring 2025, Steven Hoffman\\
    This will be a specialized course in which we shall present boundedness criteria for generalized singular integral operators and square functions (the so-called ``$T1$'' and ``$Tb$'' Theorems), as well as some of their applications, in particular, to the solution of the Kato square root problem. \\
    \textit{Textbook}: None.

    \item[] \textbf{MATH 8449}, \textit{Ordinary Differential Equations I}, Fall 2025, Konstantin Makarov\\
    Topics from existence and uniqueness theorems, plane autonomous systems, periodicity and boundedness of solutions of second order nonlinear equations, perturbation theory, Sturm-Liouville systems, behaviour of solutions at singularities. \\
    \textit{Textbook}: None.  

    \item[] \textbf{MATH 8202}, \textit{Topics in Functional Analysis: High-Dimensional Probability}, Fall 2025, Petros Valettas\\
    Topics includes concentration of measure (Cram\'{e}r-Chernoff morthod, Azuma-Hoeffding inequality, Berstain inequalities, etc), high-dimensional distributions (sub-gaussian and sub-exponential random vectors, isotropic random vectors, random matrices, etc), and random processes and chaining (Slepian's inequality, Sudakov's minoration, Dudley's inequality, etc). \\
    \textit{Textbook}: \textit{High-Dimensional Probability: An introduction with applications in data science}, 2nd edition, by Roman Vershynin.  
\end{enumerate}
\end{document}